\begin{frame}
\frametitle{Day 16: Light Propagation}
This problem asks us to illuminate as many cells of a room as possible by
shining a light from any cell on an outer edge.\vspace{3em}

This is complicated by the fact that there are mirrors and beam splitters
in the room.
\end{frame}

\begin{frame}[fragile]
\frametitle{Day 16: Rules}
If the beam encounters empty space (\verb!.!), it continues in the same direction.\vfill

If the beam encounters a mirror (\verb!/! or \verb!\!), the beam is reflected 90 degrees depending on the angle of the mirror.\vfill

If the beam encounters the pointy end of a splitter (\verb!|! or \verb!-!), the beam passes as if the splitter were empty space.\vfill

If the beam encounters the flat side of a splitter (\verb!|! or \verb!-!), the beam is split into two beams going in each of the two directions the splitter's pointy ends are pointing.\vfill

Beams do not interact with other beams
\end{frame}

\begin{frame}[fragile]
\frametitle{Day 16: Example}

\begin{center}
\begin{minipage}{0.45\textwidth}
\begin{center}
\begin{verbatim}
.|...\....
|.-.\.....
.....|-...
........|.
..........
.........\
..../.\\..
.-.-/..|..
.|....-|.\
..//.|....
\end{verbatim}
\end{center}
\end{minipage}
\begin{minipage}{0.45\textwidth}
\begin{center}
\begin{verbatim}
>|<<<\....
|v-.\^....
.v...|->>>
.v...v^.|.
.v...v^...
.v...v^..\
.v../2\\..
<->-/vv|..
.|<<<2-|.\
.v//.|.v..
\end{verbatim}
\end{center}
\end{minipage}
\end{center}
\vfill

In this example, 46 cells are {\it illuminated} when light shines in from the left in the top left cell.
\end{frame}

\begin{frame}
\frametitle{Day 16: Instance Size}

Our problem input is a room with 110 rows and 110 columns.\vfill

So there are 12100 cells.\vfill

Our instance has 1191 objects in the room.\vfill

What are the challenges of this problem?\vfill

Let's look at a solution.
\end{frame}
