\begin{frame}
\frametitle{Day 24: Never Tell Me The Odds}

You're surrounded by hailstones, each with a given position and velocity\vfill
PX, PY, PZ @ VX, VY, VZ\vfill

Part 1: Looking forward in time, how many of the hailstones' paths will intersect within a test area?\vfill

Make it simpler:
\begin{itemize}
    \item Forward in time: t $>$ 0
    \item Paths will intersect: hailstones themselves don't have to collide
    \item Within a test area: specific bounds
    \item Also, ignore the Z axis.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Day 24: Never Tell Me The Odds}

If we know a starting point and our change, what are we actually working with?\vfill % Lines

How easy is it to see if lines intersect?\vfill % Very easy

\end{frame}

\begin{frame}
\frametitle{Day 24: Never Tell Me The Odds, Continued}
    
Although the paths cross, no hailstones will actually collide on their current course. If you throw a rock just right, you can hit every hailstone! \vfill
Thanks to magic, the rock can start at any integer position and velocity. \vfill
Where and how quickly to throw the rock? \vfill
    
\end{frame}

\begin{frame}
\frametitle{Day 24: Never Tell Me The Odds, Continued}
    
Now we don't know PX, PY, PZ, VX, VY, or VZ for our rock\vfill

We do know that at some time $T$, our rock will collide with a hailstone at position $X, Y, Z$\vfill

No guarantee that $T_1$ = 1, $T_2$ = 2, etc., so $T$ is unknown.\vfill
    
\end{frame}

\begin{frame}
\frametitle{Day 24: Putting Together the Unknowns}
    
So we have 7 unknowns: PX, PY, PZ, VX, VY, VZ, and T.\vfill

What do we know?\vfill

At $T_1$, $X_{rock}, Y_{rock}, Z_{rock} = X_{hail_1}, Y_{hail_1}, Z_{hail_1}$\vfill

$Pos_T = Pos_{Start} + Velocity(T)$\linebreak
$X_{rock} = PX + VX(T)$\linebreak
$X_{hail_1} = PX_{hail_1} + VX_{hail_1}(T)$\vfill

Now we're adding in equations with known variables.

\end{frame}